CKY Parsing With Independence Constraints

### 2015-07-03 paper.tex
Add author
Adjust spacing
Improve feature table

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{acl2015}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{forest}
\usepackage[linesnumbered]{algorithm2e}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\BigO}[1]{\ensuremath{\operatorname{O}\bigl(#1\bigr)}}
\date{\today}
\title{CKY Parsing With Independence Constraints}
\begin{document}

@@

\begin{tabular}{lrrrrrrrrrr}
Features & \#feats & Acc & Prec & Rec & F$_{\text{1}}$ & F$_{\text{0.5}}$ & TP & FP & FN & TN\\
\hline
p & 37001 & 93.71 & 80.73 & 70.49 & 75.27 & 78.45 & 3679 & 878 & 1540 & 32320\\
P$_{\text{0}}$ & 33167 & 87.16 & 51.69 & 83.98 & 63.99 & 55.99 & 4383 & 4097 & 836 & 29101\\
\hline
p,P$_{\text{0}}$ & 70168 & 95.21 & 87.38 & 75.65 & 81.09 & 84.75 & 3948 & 570 & 1271 & 32628\\
p,P$_{\text{1}}$ & 37055 & 94.81 & 78.38 & 85.38 & 81.73 & 79.69 & 4456 & 1229 & 763 & 31969\\
p,P$_{\text{2}}$ & 39336 & 95.34 & 84.25 & 80.76 & 82.47 & 83.53 & 4215 & 788 & 1004 & 32410\\
p,P$_{\text{3}}$ & 46861 & 95.04 & 89.47 & 71.95 & 79.76 & 85.31 & 3755 & 442 & 1464 & 32756\\
\hline
p,P$_{\text{0}}$,P$_{\text{1}}$ & 70222 & 95.48 & 88.95 & 76.16 & 82.06 & 86.06 & 3975 & 494 & 1244 & 32704\\
p,P$_{\text{0}}$,P$_{\text{2}}$ & 72503 & 95.09 & 88.28 & 73.60 & 80.27 & 84.89 & 3841 & 510 & 1378 & 32688\\
p,P$_{\text{0}}$,P$_{\text{3}}$ & 80028 & 94.84 & 88.81 & 70.99 & 78.91 & 84.56 & 3705 & 467 & 1514 & 32731\\
\hline
p,P$_{\text{1}}$,P$_{\text{2}}$ & 39390 & 95.27 & 80.99 & 85.21 & 83.04 & 81.80 & 4447 & 1044 & 772 & 32154\\
p,P$_{\text{1}}$,P$_{\text{3}}$ & 41553 & 95.44 & 89.05 & 75.74 & 81.86 & 86.03 & 3953 & 486 & 1266 & 32712\\
\hline
p,P$_{\text{0}}$,P$_{\text{1}}$,P$_{\text{2}}$,P$_{\text{3}}$ & 82417 & 95.35 & 86.89 & 77.49 & 81.92 & 84.83 & 4044 & 610 & 1175 & 32588\\
\end{tabular}

%}
\caption{Results of classifier using different combinations of features.}
\label{tbl:feature-evaluation}
\end{table*}

>>>>

\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{fixltx2e}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{float}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{amssymb}
\usepackage{acl2015}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{forest}
\usepackage[linesnumbered]{algorithm2e}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\BigO}[1]{\ensuremath{\operatorname{O}\bigl(#1\bigr)}}
\newcommand{\Dag}{\ensuremath{^{\dagger}}}

\title{CKY Parsing With Independence Constraints}
\author{Joseph Irwin \\
  Graduate School of Information Science\hspace{1em} \\
  Nara Institute of Science and Technology\hspace{1em} \\
  {\tt joseph-i@is.naist.jp} \\\And
  Yuji Matsumoto \\
  Graduate School of Information Science \\
  Nara Institute of Science and Technology \\
  {\tt matsu@is.naist.jp} \\}

\begin{document}

@@

\begin{tabular}{lrrrrrrrrrr}
{\bf Features} & {\bf \#feats} & {\bf Acc} & {\bf Prec} & {\bf Rec} & {\bf F$_{\text{1}}$} & {\bf F$_{\text{0.5}}$} & {\bf TP} & {\bf FP} & {\bf FN} & {\bf TN} \\
\hline
p & 37001 & 93.71 & 80.73 & 70.49 & 75.27 & 78.45 & 3679 & 878 & 1540 & 32320\\
P$_{\text{0}}$ & 33167 & 87.16 & 51.69 & 83.98 & 63.99 & 55.99 & 4383 & 4097 & 836 & 29101\\
\hline
p,P$_{\text{0}}$ & 70168 & 95.21 & 87.38 & 75.65 & 81.09 & 84.75 & 3948 & 570 & 1271 & 32628\\
p,P$_{\text{1}}$ & 37055 & 94.81 & 78.38 & 85.38 & 81.73 & 79.69 & 4456 & 1229 & 763 & 31969\\
p,P$_{\text{2}}$ & 39336 & 95.34 & 84.25 & 80.76 & 82.47 & 83.53 & 4215 & 788 & 1004 & 32410\\
p,P$_{\text{3}}$ & 46861 & 95.04 & 89.47 & 71.95 & 79.76 & 85.31 & 3755 & 442 & 1464 & 32756\\
\hline
p,P$_{\text{0}}$,P$_{\text{1}}$ & 70222 & {\bf 95.48} & {\bf 88.95} & 76.16 & 82.06 & {\bf 86.06} & 3975 & 494 & 1244 & 32704\\
p,P$_{\text{0}}$,P$_{\text{2}}$ & 72503 & 95.09 & 88.28 & 73.60 & 80.27 & 84.89 & 3841 & 510 & 1378 & 32688\\
p,P$_{\text{0}}$,P$_{\text{3}}$ & 80028 & 94.84 & 88.81 & 70.99 & 78.91 & 84.56 & 3705 & 467 & 1514 & 32731\\
\hline
p,P$_{\text{1}}$,P$_{\text{2}}$ & 39390 & 95.27 & 80.99 & 85.21 & {\bf 83.04} & 81.80 & 4447 & 1044 & 772 & 32154\\
p,P$_{\text{1}}$,P$_{\text{3}}$$^{*}$ & 41553 & {\bf 95.44} & {\bf 89.05} & 75.74 & 81.86 & {\bf 86.03} & 3953 & 486 & 1266 & 32712\\
\hline
p,P$_{\text{0}}$,P$_{\text{1}}$,P$_{\text{2}}$,P$_{\text{3}}$ & 82417 & 95.35 & 86.89 & 77.49 & 81.92 & 84.83 & 4044 & 610 & 1175 & 32588\\
\end{tabular}

%}
\caption{Results of classifier using different combinations of features.
($^{*}$Final feature configuration.)}
\label{tbl:feature-evaluation}
\end{table*}
